Instructions for developing new pages for the MarineOmics webpage

### 2023-12-14 DRAFT_DNA_methylation.Rmd
more on bismark genome prep

Bismark will create the following subdirectories as outputs of the above code for genome preparation

>>>>

Bismark will create two individual folders within this directory, one for a C->T converted genome and the other one for the G->A converted genome. After creating C->T and G->A versions of the genome they will be indexed in parallel usingthe indexer. Bismark will create the following subdirectories as outputs.
